---
title: "Cabbages"
author: Mariahlynn Woolfolk
date: May 21,2024
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  


%H_0$: There is no difference in the average Vitamin c content of cabbages based on cultivation method. 

$H_A%: There is a difference in the average vitamin c content.

# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Vitamin c is numerical,cultivation is categorical 

numerical~categorical so we use the numerical~cat helper file


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results 

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult, data=veggy)
```
The boxplot shows that cultivation method C52 generally has more VitC than C39

### Numerical Descriptive results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The numerical summary shows that the C52 has more VitC than the C39

## Inferential Results

```{r}
t.test(VitC~Cult,data=veggy)
```

The P-value is so small we wpuld reject the null hypothesis. 

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, suchas test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions which the selected test/procedure satisfys the assumptions and is appropriate to answer the research!-->

# Discussilon and Conclusion 


<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the varibles causes the other, or whether they perhaps are related for some other reason. Watch the chapter 6 videos from the Georgetown videos collection.!-->








